\begin{frame}
\frametitle{Introduction}
\begin{itemize}
	\item Feature Subset Selection (FSS) for supervised learning.
	\begin{itemize}
		\pause
		\item Identifies relevant features for building robust learning models.
		\item Allows domain experts to get focused on the relevant part of a problem. 
		\item Increase the generalization capabilities for predictor models in classifications task.
	\end{itemize}
	\pause
	\item Estimation of distribution algorithms
	\begin{itemize}
		\pause
		\item Finds optimal solutions for complex search problems.
		\pause
		\item The solution is represented by probability distribution model.
		\pause
		\item Could be used as a FSS to find relevant variables.
	\end{itemize}
\end{itemize}
\end{frame}
\begin{frame}
\frametitle{Introduction}
\begin{itemize}
	\item Kernel Classifiers
	\pause
	\begin{itemize}
		\item Kernel classifiers  have recently emerged as powerful high-accuracy classifiers with robust generalization abilities.
		\item Use \emph{Kernel} functions as a mappings of similarity measures in a transformed space where nonlinearities can be solved linearly.
		\item Two widely used kernel functions are: \pause
					\begin{equation}
					K_{\sigma}(\bar{x},\bar{z}) = \text{exp}\Big( -\sigma\sum_{k} (x_k-z_k)^2 \Big)
					\label{eq:eq01}
				\end{equation} and
				\begin{equation}
					K_d(\bar{x},\bar{z}) = \langle \bar{x}, \bar{z} \rangle^d,
					\label{eq:eq02}
				\end{equation}

	\end{itemize}
\end{itemize}
\end{frame}